Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Small changes.

\ldots

@@

Traffic obfuscation has been approached in many different ways,
which may be classified into two general techniques.
The first technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Classic example of look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but it takes additional steps to obscure its traffic signature
(packet lengths and timing), and is designed to resist active scanning for proxies
(the proxy server remains silent until the client proves knowledge of a shared
secret).

@@

\cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is not clear whether ISPs are
willing to act against censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

CloudTransport~\cite{cloudtransport}

@@

\section{Security}

>>>>

@@

Traffic obfuscation has been approached in many different ways,
which may be classified into two general techniques.
The first technique is to look unlike
anything forbidden by the censor; that is, fail to match a blacklist. The second is
to resemble a protocol that is explicitly allowed by the censor; that is, match a whitelist.
Falling into the first category are ``look-like-nothing'' transports whose
payloads are indistinguishable from a uniformly random byte stream.
Classic example of look-like-nothing
protocols are obfs2~\cite{obfs2} and its successor obfs3~\cite{obfs3},
which have been Tor's go-to pluggable transports since early 2012~\cite{obfsproxy-arms-race}.
ScrambleSuit~\cite{scramblesuit} is like obfs3 in the
content of its payloads, but it takes additional steps to obscure its traffic signature
(packet lengths and timing), and is designed to resist active scanning
(the proxy server remains silent until the client proves knowledge of a shared
secret).

@@

% \cite{ccs2012-decoys}
% Routing around decoys
A recent study~\cite{nodirectionhome} on AS
topology suggests that defeating decoy routing is likely to be expensive for the
censors, if the decoy routers are strategically deployed. Despite that decoy
routing is a sound technical approach, it is not clear whether ISPs are
willing to act against censors. However, the takeaway is that the
censors are unwilling to completely block day-to-day Internet access, which we
can take advantage of.

% CloudTransport~\cite{cloudtransport}

@@

% \section{Security}
